Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-02-01 automatica/paper.tex
overall paper

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures} are indicated by~\xmark.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.

>>>>

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures; 
From Section 7: ``
otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
then the synthesis is considered to have \emph{failed}
''} are indicated by~\xmark.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.
